Incentivizing Exploration by Heterogeneous Users

### 2018-02-12 algorithm.tex
did some minor changes to the paper

\begin{lemma} \label{lem:phase-length}
For any $s$, the expected length of phase $s$ is at most
$\ARMNUM \cdot s$ time steps.
\end{lemma}

@@

In the high-probability case
$|S_J| \leq
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}$,
we first use that $\sqrt{\cdot}$ is sublinear to bound
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.
Then, we use the following technical Lemma~\ref{lem:n0-inequality}
(whose proof is given in the appendix, and whose precondition we verify
momentarily) to bound the first term,
giving us an overall upper bound of
$|S_J| \leq \frac{J x}{2 \sigma}$.

@@

\begin{align*}
\lefteqn{\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR}
\\ & =
\sum_{s = 1}^T 
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
  \cdot \Expect{\mbox{Length of phase } s}
\\ & \leq
\sum_{s = 1}^T 
 \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
  \cdot \ARMNUM s,
\end{align*}
where the inequality was an application of Lemma~\ref{lem:phase-length}.
Adding all three terms,
the cumulative regret up to time $T$ is at most

\begin{align}
&O \left( \MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right)
\\
+ & \sum_{s = 1}^T 
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
  \cdot \ARMNUM s,
+ \sum_{s=1}^{T}\TieDensity \cdot g^2(s)\cdot N\log(s). \label{thm:equ}
\end{align}

@@

\begin{align*}
\lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  +
          \frac{288\ARMNUM\Diam^2 d^2\sigma^2
          \TieDensity\log(T)}{1.8}\sum_{s=1}^{T}\frac{\log(s)}{s}}
\\ & \leq
24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 160 \ARMNUM \Diam^2 d^2\sigma^2
          \TieDensity(\log(T))^2(\log(T)+1)
  \\ & \leq
12 \ARMNUM^2 d R  + 160 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^2(\log(T)+1). 
\end{align*}

@@

\begin{corollary} \label{cor:constant-regret}
If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(\ARMNUM^2)$.
\end{corollary}

\begin{proof}
The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}. If we set $g^2(s) = \frac{288\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$, then there exists a $s^{0}$ such that for $s>s_{0}$, $q(g(s))=0$. Thus, similar to equation~\eqref{thm:equ}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
\begin{align}
\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)+ \sum_{s=1}^{s^{0}}\TieDensity g(s)^2\ARMNUM\log(s) \nonumber
\end{align}
Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(\ARMNUM^2)$.
\end{proof}

@@

In Algorithm~\ref{alg:basic-incentivizing},
the payment \Pay{t}{i} offered for pulling payment-eligible arms $i$
is high enough to ensure that arm $i$ will be pulled with probability 1.
However, as can be seen in the proof of Lemma~\ref{lem:phase-length},
we then lower-bound this probability by $1/s$.
Thus, the bounds we prove do not deteriorate as long as the payment is
high enough such that arm $i$ is pulled with probability at least $1/s$.
A sufficient payment would be defined as
$\Pay{t}{i} = \sup \Set{c \geq 0}{%
  \Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \leq \AgV \cdot \ArmEV{t}{i'}}}$.
Except for offering different payments, the algorithm remains unchanged.
Then, the exact same analysis shows that the modified algorithm
provides the same guarantees.

>>>>

\begin{lemma} \label{lem:phase-length}
For any $s\geq 3$, the expected length of phase $s$ is at most
$\ARMNUM \cdot \log(s)$ time steps.
\end{lemma}

@@

In the high-probability case
$|S_J| \leq
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}$,
we first use that $\sqrt{\cdot}$ is sublinear to bound
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.

\bccomment{If $b(n)$ is a constant, here we know $\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{\sqrt{J} x}{4 \sigma}\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.}

Then, we use the following technical Lemma~\ref{lem:n0-inequality}
(whose proof is given in the appendix, and whose precondition we verify
momentarily) to bound the first term,
giving us an overall upper bound of
$|S_J| \leq \frac{J x}{2 \sigma}$.

@@

\begin{align*}
\lefteqn{\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR}
\\ & =
\sum_{s = 1}^T 
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
  \cdot \Expect{\mbox{Length of phase } s}
\\ & \leq
\sum_{s = 1}^T 
 \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
  \cdot \ARMNUM \log(s),
\end{align*}
where the inequality was an application of Lemma~\ref{lem:phase-length}.
Adding all three terms,
the cumulative regret up to time $T$ is at most

\begin{align}
&O \left( \MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right)
\\
+ & \sum_{s = 1}^T 
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
  \cdot \ARMNUM \log(s),
+ \sum_{s=1}^{T}\TieDensity \cdot g^2(s)\cdot N\log(s). \label{thm:equ}
\end{align}

@@

\begin{align*}
\lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d \log(s) \MAXR \exp\left(-2\log(T)\right)  +
          \frac{288\ARMNUM\Diam^2 d^2\sigma^2
          \TieDensity\log(T)}{1.8}\sum_{s=1}^{T}\frac{\log(s)}{s}}
\\ & \leq
24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 160 \ARMNUM \Diam^2 d^2\sigma^2
          \TieDensity(\log(T))^2(\log(T)+1)
  \\ & \leq
12 \ARMNUM^2 d R  + 160 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^2(\log(T)+1). 
\end{align*}

@@

\begin{corollary} \label{cor:constant-regret}
If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right) $.
\end{corollary}

\begin{proof}
The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}. If we set $g^2(s) = \frac{288\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$, then there exists a $s^{0}$ such that for $s>s_{0}$, $q(g(s))=0$. Thus, similar to equation~\eqref{thm:equ}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
\begin{align}
\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)+ \sum_{s=1}^{s^{0}}\TieDensity g(s)^2\ARMNUM\log(s) \nonumber
\end{align}
Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right) $.
\end{proof}

@@

In Algorithm~\ref{alg:basic-incentivizing},
the payment \Pay{t}{i} offered for pulling payment-eligible arms $i$
is high enough to ensure that arm $i$ will be pulled with probability 1.
However, as can be seen in the proof of Lemma~\ref{lem:phase-length},
we then lower-bound this probability by $1/\log(s)$.
Thus, the bounds we prove do not deteriorate as long as the payment is
high enough such that arm $i$ is pulled with probability at least $1/\log(s)$.
A sufficient payment would be defined as
$\Pay{t}{i} = \sup \Set{c \geq 0}{%
  \Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \leq \AgV \cdot \ArmEV{t}{i'}}}$.
Except for offering different payments, the algorithm remains unchanged.
Then, the exact same analysis shows that the modified algorithm
provides the same guarantees.

### 2018-02-12 appendix.tex
did some minor changes to the paper

Denote $\mathcal{F}_t$ as the filtration up to time $t$. Denote $V_t$ as the set of arms that we need to pull, but haven't pulled yet in this phase. Based on our algorithm, we know

\[ \Prob{\text{play a new arm}|\mathcal{F}_t} =
\begin{cases}
1       & \quad \text{if we incentivize}\\
\sum_{i\in V} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{otherwise}  
\end{cases} \label{dom_stoc}
\] 
\hspace{1cm}$\geq (\ARMNUM-|V_t|)\times \frac{1}{\log(s)}$.
\bccomment{probably we need to be more careful about $\frac{1}{\log(s)}$}.
Let $(Z_{s,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $\frac{\ARMNUM-v}{\log(s)}$. We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
\begin{align}
t_{s}-t_{s-1}\leq \bar{T}_{s}:=\sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}, \nonumber 
\end{align}
where $\bar{T}_{s,v}:=\inf\{m\geq 0: Z_{s,v,m}=1\}+1$.

@@

If $Z_{s,v(s,t),m(s,t)}$ is 1, decide to play a new arm. Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-(1-\frac{v(s,t)}{s})}{1-(1-\frac{v(s,t)}{s})}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm. Note that

>>>>

Denote $\mathcal{F}_t$ as the filtration up to time $t$. Denote $V_t$ as the set of arms that have been pulled at least $s$ times at time $t$ in phase $s$. Based on our algorithm, we know

\[ \Prob{\text{play a new arm}|\mathcal{F}_t} =
\begin{cases}
1       & \quad \text{if we incentivize}\\
\sum_{i\in \{1,\cdots,\ARMNUM\}\setminus V_t} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{otherwise}  
\end{cases} \label{dom_stoc}
\] 
\hspace{1cm}$\geq (\ARMNUM-|V_t|)\times \frac{1}{\log(s)}$.
\bccomment{probably we need to be more careful about $\frac{1}{\log(s)}$}.
Let $(Z_{s,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $\frac{\ARMNUM-v}{\log(s)}$. We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
\begin{align}
t_{s}-t_{s-1}\leq \bar{T}_{s}:=\sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}, \nonumber 
\end{align}
where $\bar{T}_{s,v}:=\inf\{m\geq 0: Z_{s,v,m}=1\}+1$.

@@

If $Z_{s,v(s,t),m(s,t)}$ is 1, decide to play a new arm. Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-\frac{\ARMNUM-v(s,t)}{\log(s)}}{1-\frac{\ARMNUM-v(s,t)}{\log(s)}}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm. Note that
